PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-24 qfenv_paper/qf_environment.tex
More discussions on QF and additions to the SMF.

Finally we measure the environment for each galaxy in our sampling by counting the number of EDP galaxies, $n_{\rm{env}}$ with $RA$, $Dec$, and $z$ within our cylindrical aperture centered around it. Note that $n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies. Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 1$ to be "low" environment density and galaxies with $n_{\rm{env}} > 3$ to be "high" environment densities. The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient

@@

We present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels) in Figure \ref{fig:smf}. The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The sample variance uncertainties are incorporated in the width of the SMFs.

@@

%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. 
%Remark on the clear mass-density relation: more massive galaxies in high environment 
% Compare to Bolzonella et al. 2010 and perhaps even Bundy et al. 2006 results
% Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (CITECITE).

@@

In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass,

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa}. For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions. %Color-density dependence in Cucciati?

The same fitting procedure was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as \ref{fig:qffit}. Increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ also does not change the total evolution for either environments. In contrast, as mentioned above, \cite{Iovino:2010aa} finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$. Furthermore, changing the fiducial mass does not significant change the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ between the environments. This is again in disagreement with \cite{Iovino:2010aa}, which finds a significant redshift dependent difference in $f_{\rm{blue}}$ between group and isolated galaxies at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, but finds no difference at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$. As suggested earlier, our $f_{\rm{Q}}$ results show little mass dependence in our $f_{\rm{Q}}$ evolution. Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

Finally, from Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly, it quantifies the total evolution of $f_{\rm{Q}}$ since $z \sim 0.8$ for both low and high density environments. Remarkably, the $f_{\rm{Q}}$ evolves by the same amount for both environments. In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence. This disagrees with the $f_{\rm{blue}}$ results from \cite{Iovino:2010aa}, which show a clear distinction between group and isolated galaxies. In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies. At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from z~0.6 to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment. 
% Considering our definition of environment may be susceptible to contamination, we considered more stringent classification of both low and high density environments. However,

The analysis described in this paper use a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment, the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$). The results obtained from using these different are consistent with the results displayed in this paper.

@@

%
% References
%
\bibliography{PRIMUS}

>>>>

Finally we measure the environment for each galaxy in our sampling by counting the number of EDP galaxies, $n_{\rm{env}}$ with $RA$, $Dec$, and $z$ within our cylindrical aperture centered around it. Note that $n_{\rm{env}}$ accounts for the statistical weights of the EDP galaxies. Once we obtain environment measurements for all the galaxies in our galaxy sample, we classify galaxies with $n_{\rm{env}} < 1$ to be "low" environment density and galaxies with $n_{\rm{env}} > 3$ to be "high" environment densities. The high environment cutoff was selected in order to reduce contamination from galaxies in low environment densities while maintaining sufficient statistics.

The analysis we describe below uses a fixed cylindrical aperture with dimensions $R_{\rm{ap}} = 2 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25 \: \rm{Mpc}$ to measure environment; the same analysis was extended for varying aperture dimensions $R_{\rm{ap}} = 1, 2, 3 \: \rm{Mpc}$ and $H_{\rm{ap}} = 25, 50 \: \rm{Mpc}$. Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$). The results obtained from using these different are consistent with the results later discussed in this paper.

@@

In Figure \ref{fig:smf}, we present the SMFs for 16 target galaxy subsamples classified into quiescent/star-forming (orange/blue, bottom/top panels) and high/low environment density (left/right panels). The redshift evolution of the SMFs in each of these panels are indicated by a darker shade for lower redshift bins. The sample variance uncertainties are illustrated through the width of the SMFs.

In order to consistently measure environment throughout our entire sample we impose PRIMUS redshift errors on our SDSS galaxies. However, we observe a significant difference between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. 
As a result, we note that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe certain trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.

@@

%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. 
%Remark on the clear mass-density relation: more massive galaxies in high environment 
% Compare to Bolzonella et al. 2010 and  Bundy et al. 2006 results
% Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).

@@

In order to more quantitatively compare the $f_{\rm{Q}}$ evolution, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}

@@

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions. As galaxy color and SFR are related, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) in favor of the idea that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).

The same fitting procedure was performed using $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$; however, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, just as Figure \ref{fig:qffit}. Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not change the total evolution for either environments. On the other hand, \cite{Iovino:2010aa}, for both group and isolated galaxies, finds significantly less $f_{\rm{Q}}$ evolution for $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ than in $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$. Furthermore, \cite{Iovino:2010aa} also finds that the difference in $f_{\rm{blue}}$ evolution between group and isolated galaxies ($f_{\rm{blue}, \rm{isolated}}(z) - f_{\rm{blue}, \rm{group}}(z))$ is much greater at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find almost no difference. In contrast, we find that changing the fiducial mass does not significantly alter the difference in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$. The zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is change reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence. Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

Finally, from Figure \ref{fig:qffit}, we note that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly, we quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments. Remarkably, $f_{\rm{Q}}$ evolves by the same amount for both environments. In other words, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show little environment dependence. This disagrees with the $f_{\rm{blue}}$ results from \cite{Iovino:2010aa}, which show a clear distinction between group and isolated galaxies. In \cite{Iovino:2010aa}, $f_{\rm{blue}}$ for isolated galaxies decrease much faster than $f_{\rm{blue}}$ for group galaxies. At $\mathcal{M} \sim 10.5$, \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ for isolated galaxy decreases by 0.3 from $z \sim 0.6$ to 0.3, while for $f_{\rm{blue}}$ for group galaxies only decrease by 0.1 in the same redshift limit, showing a clear dependence in environment. Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$. While a more stringent classification increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall as well as the uncertainties, it does not reveal reveal any significant environment dependence in the $f_{\rm{Q}}$ evolution. Therefore, the potential contamination in our environment measurements cannot explain the lack of environment dependence in the $f_{\rm{Q}}$ evolution.

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Often star-formation quenching is parameterized using two distinct mechanisms: mass-dependent and environment dependent mechanisms (Baldry et al. 2006 Peng et al. 2010). By the mass-dependence in all $f_{\rm{Q}}$ in Figure \ref{fig:qf} we conclude that galaxy stellar mass plays a significant role in quenching. Furthermore, from the fact that $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching. However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease. This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$. We find that this is not the case. % What does this have to say about physical processes in groups and clusters that affect quenching?

@@

We thank ...
%
% References
%
\bibliography{PRIMUS}
